### 2017-08-10 Paper01_EnthalpyAndCrystallization.tex
Results - dynamic xrd - minor edits, change crystallisation to Aus S spelling

%Title
\textbf{\LARGE{An assessment of structural enthalpy and crystallization pathways of \MgZnCa~ bulk metallic glass and amorphous films}}

@@

The structural nature and thermal stability of amorphous alloys is highly dependent on the method by which they are produced, i.e. their relaxation rate upon cooling.  Both bulk samples and metallic glass films of \MgZnCa~ were produced by copper mold casting and \gls{dc} magnetron sputtering onto aluminium substrates, respectively. Comparisons between structural enthalpy, crystallization pathways, relaxation and crystallization kinetics of the bulk samples and films were examined by elevated temperature \acrshort{xrd} and \acrshort{dsc}. Compared with equivalent experiments on the bulk alloy, results for the thin films show distinct differences in structural enthalpy and deviations from the expected crystalline phase evolution, displaying minor peak shifts, failure of some phases to evolve, and variations in the evolution rates.

@@

\subsection{Master alloy}
The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere. Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for injection and gravity casting respectively. Bulk amorphous \MgZnCa~ rods of $2.5 mm$ diameter and plates of thickness of $XX \mu m$ were produced by copper mold injection casting. The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity castings sectioned to thicknesses of $3.25 mm$. All samples and targets were stored under Ar when not being examined or used.

@@

The deconvolution fits were integrated to find the area under each curves. This information provides the \gls{h} of the crystallization of each phase. This is presented in Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy} for the bulk and film respectively. Figure \ref{fig:DSC_Decon} shows the \Tx~ onsets and \acrfull{h} for both the bulk and film plotted together.

@@

From these experiments 5 previously observed crystallisation phases of the MgZnCa system \cite{Zhang2013, Zhang2012, Zhang2011, Khan1989, Cao2016} were characterised in the bulk and film \MgZnCa. This allowed the crystallization process of \MgZnCa~ from the fully amorphous glass to fully crystalline metal to be identified as;

@@

In Figures \ref{fig:XRD_Annealing_Bulk} and \ref{fig:XRD_Annealing_Film} it can be observed that Mg$_{51}$Zn$_{20}$ comes out at lower temperature in the film compared to the bulk, while the other phase nucleate and grow at similar rates for both the bulk and film. The temperature each phase is first and last observed are tabulated in Table \ref{tab:Crystal_Sequence}.

@@

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.85\textwidth]{XRD_Annealing_Bulk.png}
	\caption[Table of contents Capition]{\acrshort{xrd} pattern for bulk \MgZnCa~ heated treated to several temperatures for crystallization peak identified from \acrshort{dsc}.}
	\label{fig:XRD_Annealing_Bulk}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.85\textwidth]{XRD_Annealing_Film.png}
	\caption[Table of contents Capition]{\acrshort{xrd} pattern for film \MgZnCa~ heated treated to several temperatures for crystallization peak identified from \acrshort{dsc}. Note the Al substrate peaks have been faceted as to not dwarf all other peaks.}
	\label{fig:XRD_Annealing_Film}
\end{figure}

@@

The annealing \acrshort{xrd} was useful for identifying the crystal phases present, but not many difference between the evolution rates of the bulk or films could be observed. Thus samples were subjected to dynamic \acrshort{xrd} over their most active rang to observe changes \textit{in-situ}. This allowed the crystallisation to be watched live for seeing how phase evolved over time as the temperature was raised in 5 \degree C increments.

@@

The use of a 60K \gls{dsc} heating rate compared to the more commonly used 20K rate [sources] shifts peaks for the bulk \MgZnCa~ alloy about 8 - 15 degrees higher. This higher heating rates were used because crystallization events for the films were difficult to differentiation at the lower heating rate. 
Films show little shift to high temperature peaks with increases heating rates, but large shifts with relaxation. 
Bulk show the opposite behaviour, larger peaks shifts with higher heating rates and little shift with relaxation.

>>>>

%Title
\textbf{\LARGE{An assessment of structural enthalpy and crystallisation pathways of \MgZnCa~ bulk metallic glass and amorphous films}}

@@

The structural nature and thermal stability of amorphous alloys is highly dependent on the method by which they are produced, i.e. their relaxation rate upon cooling.  Both bulk samples and metallic glass films of \MgZnCa~ were produced by copper mold casting and \gls{dc} magnetron sputtering onto aluminium substrates, respectively. Comparisons between structural enthalpy, crystallisation pathways, relaxation and crystallisation kinetics of the bulk samples and films were examined by elevated temperature \acrshort{xrd} and \acrshort{dsc}. Compared with equivalent experiments on the bulk alloy, results for the thin films show distinct differences in structural enthalpy and deviations from the expected crystalline phase evolution, displaying minor peak shifts, failure of some phases to evolve, and variations in the evolution rates.

@@

\subsection{Master alloy}
The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared with an in-house induction melting furnace within boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere. Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for injection and gravity casting respectively. Bulk amorphous \MgZnCa~ rods of $2.5 mm$ diameter and plates of thickness of $XX \mu m$ were produced by copper mold injection casting. The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity castings sectioned to thicknesses of $3.25 mm$. All samples and targets were stored under Ar when not being examined or used. 
\todo{measure injection plate thickness with micrometer}

@@

The deconvolution fits were integrated to find the area under each curves. This information provides the \gls{h} of the crystallisation of each phase. This is presented in Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy} for the bulk and film respectively. Figure \ref{fig:DSC_Decon} shows the \Tx~ onsets and \acrfull{h} for both the bulk and film plotted together.

@@

From these experiments 5 previously observed crystallisation phases of the MgZnCa system \cite{Zhang2013, Zhang2012, Zhang2011, Khan1989, Cao2016} were characterised in the bulk and film \MgZnCa. This allowed the crystallisation process of \MgZnCa~ from the fully amorphous glass to fully crystalline metal to be identified as;

@@

In Figures \ref{fig:XRD_Annealing_Bulk} and \ref{fig:XRD_Annealing_Film} it can be observed that Mg$_{51}$Zn$_{20}$ comes out at lower temperature in the film compared to the bulk, while the other phases nucleate and grow at similar rates for both the bulk and film. The temperature each phase is first and last observed are tabulated in Table \ref{tab:Crystal_Sequence}.

@@

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.85\textwidth]{XRD_Annealing_Bulk.png}
	\caption[Table of contents Capition]{\acrshort{xrd} pattern for bulk \MgZnCa~ heated treated to several temperatures for crystallisation peak identified from \acrshort{dsc}.}
	\label{fig:XRD_Annealing_Bulk}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.85\textwidth]{XRD_Annealing_Film.png}
	\caption[Table of contents Capition]{\acrshort{xrd} pattern for film \MgZnCa~ heated treated to several temperatures for crystallisation peak identified from \acrshort{dsc}. Note the Al substrate peaks have been faceted as to not dwarf all other peaks.}
	\label{fig:XRD_Annealing_Film}
\end{figure}

@@

The annealing \acrshort{xrd} was useful for identifying the crystal phases present, but not many difference between the evolution rates of the bulk or films could be observed. Thus samples were subjected to dynamic \acrshort{xrd} over their most active range of $31-60$\degree~ to observe changes \textit{in-situ}. This allowed the crystallisation to be actively observed over the range of $35-185$ \degree C, showing how phases evolved over time as the temperature was raised in 5\degree C increments.

@@

The use of a 60K \gls{dsc} heating rate compared to the more commonly used 20K rate [sources] shifts peaks for the bulk \MgZnCa~ alloy about 8 - 15 degrees higher. This higher heating rates were used because crystallisation events for the films were difficult to differentiation at the lower heating rate. 
Films show little shift to high temperature peaks with increases heating rates, but large shifts with relaxation. 
Bulk show the opposite behaviour, larger peaks shifts with higher heating rates and little shift with relaxation.
